Generating and modifying matrices

### 2017-09-19 Analysis/Character_difference/Modifying_matrices.Rmd
Modifying matrices figure updated

<!-- ```{r, fig.width=12, fig.height=12}
par(mfrow = c(2, 3), bty = "n", mar = c(1,1,1,1))
## Tree
plot(tree, cex = 0.8, main = "A - Simulated tree")
## Normal matrix
plot(char_diff_matrix_norm, type = "matrix", main = "B - Normal matrix", legend = FALSE)
## Empty plot
plot(0,0, col = "white", xaxt = 'n', yaxt = 'n', xlab = "", ylab = "")
## Maximised matrix
plot(char_diff_matrix_maxi, type = "matrix", main = "C - Maximised matrix", legend = FALSE)
## Minimised matrix
plot(char_diff_matrix_mini, type = "matrix", main = "D - Minimised matrix", legend = FALSE)
## Randomised matrix
plot(char_diff_matrix_rand, type = "matrix", main = "E - Randomised matrix", legend = FALSE)
```
 -->

>>>>

```{r, fig.width=12, fig.height=12, eval = FALSE, echo = FALSE}
pdf("../../Writing/Figures/Modif_matrix.pdf", width = 7.2, height = 4.5)
par(mfrow = c(2, 3), bty = "n", mar = c(1,1,1,1))
## Tree
plot(tree, cex = 0.8, main = "A - Simulated tree")
## Normal matrix
plot(char_diff_matrix_norm, type = "matrix", main = "B - Normal matrix", legend = FALSE)
## Empty plot
plot(0,0, col = "white", xaxt = 'n', yaxt = 'n', xlab = "", ylab = "")
## Maximised matrix
plot(char_diff_matrix_maxi, type = "matrix", main = "C - Maximised matrix", legend = FALSE)
## Minimised matrix
plot(char_diff_matrix_mini, type = "matrix", main = "D - Minimised matrix", legend = FALSE)
## Randomised matrix
plot(char_diff_matrix_rand, type = "matrix", main = "E - Randomised matrix", legend = FALSE)
dev.off()
```
